---
title: "statistical inference project coursera"
author: "Abhishek Dubey"
date: "4/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Objective
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. Investigate the distribution of averages of 40 exponentials over a thousand simulations.


```{r}
#
set.seed(12323)
lambda <- 0.2
n <- 40
simulations <- 1000

# simulate
simdata <- matrix(rexp(simulations * n, rate=lambda), simulations)

# calculate mean of exponentials
simdata_means <- apply(simdata, 1, mean)
hist(simdata_means, col="green")
```

### 1. Show the sample mean and compare it to the theoretical mean of the distribution.
```{r}
#Mean of exponential distribution is 1/lambda

mean_exp_dist <- 1/lambda
print (paste("Theoretical center of the distribution = ", mean_exp_dist))

print (paste("Actual center of the distribution based on the simulations = ", round(mean(simdata_means), 2)))

```
### 2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}

theoretical_variance <- (1/lambda)^2/n
print (paste("Theoretical variance = ", theoretical_variance))

print (paste("Actual variance = ", round(var(simdata_means), 3)))
```

### 3. Show that the distribution is approximately normal.
```{r}
plotdata <- data.frame(simdata_means)
m <- ggplot(plotdata, aes(x = simdata_means))
m <- m + geom_histogram(aes(y=..density..), colour="black", fill = "blue")
m + geom_density(colour="red", size=1)

# compare the distribution of averages of 40 exponentials to a normal distribution
qqnorm(simdata_means)
qqline(simdata_means, col = 2)

```